---
author: Clement Guillo
title: Data Scientist
format:
  classic-cv-pdf: default
cvfooter:
  left: ""
  right: ""
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Head of Statistical Service at French NSI, INSEE - French Caribbean.
    right: Guadeloupe, France
  - title: Field
    left: Data Science, Statistical Methods, Spatial Analysis 
    right: /in/clgui23
  - left:  +33 6 19 93 25 36
    right: github.com/clement2323  
execute:
  echo: false
---

```{r}

#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}

cvskills <- function(tbl, category, skills) {
    command_start <- "\\cvskills"

    # Agrège les skills par catégorie
    unique_categories <- unique(tbl[[category]])
    
    res <- sapply(unique_categories, function(cat) {
        skills_list <- tbl[tbl[[category]] == cat, ][[skills]]
        skills_formatted <- paste0("{", paste(skills_list, collapse = "},{"), "}")
        
        paste0(
            command_start,
            "{", cat, "}",
            "{", skills_formatted, "}"
        )
    })

    cat(res, sep = "\n")
}
```



# Profile

Innovative Data Scientist with a strong foundation in spatial statistics, machine learning, and big data processing. Extensive experience developing and deploying data-driven solutions, including deep learning applications for satellite imagery analysis and automation of complex workflows. Actively seeking opportunities to join data science teams and driving innovation and tackling complex challenges in California’s dynamic tech ecosystem.

# Professional Experience

```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Head of Statistical Service", "INSEE French Caribbean (Guadeloupe, Martinique, Guiana)", "09/2023 - Present",
    "Guadeloupe, France", c(
        "Developed and applied deep learning algorithms for population census by processing thousands of satellite images of overseas territories (including Réunion and Mayotte). Delivered a trained segmentation model based on these images and deployed the results through an application to support population census estimates.",
        "Streamlined and automated production practices, coordinating all local teams.",
        "Managed INSEE agents, overseeing the coordination and execution of on-the-ground survey operations.",
        "Designed an R training program, aimed at improving the skills of 20 agents."
    ),
    "Head of Spatial Statistics \\& Data Confidentiality Methods", "INSEE - Paris", "09/2019 - 08/2023",
    "Paris, France", c(
        "Managed a team of 4 and supervised 3 interns specializing in satellite images analysis.",
        "Developed deep learning models achieving high accuracy in satellite image segmentation for land cover detection.",
        "Directed the redesign of a georeferencing system impacting 30 million address records.",
        "Designed and implemented an algorithm to ensure the confidentiality of gridded data across France, addressing differentiation attacks and enabling large-scale data dissemination.",
        "Supervised statistical disclosure control for 10 public annual INSEE surveys.",
        "Collaborated with European countries in working groups to harmonize methodologies for spatial analysis and statistical disclosure control at the European level."
    ),
    "Data Science Intern", "WESTAT - Rockville MD, USA", "07/2019 - 09/2019",
    "Rockville, Maryland, USA", c(
        "Analyzed large-scale imbalanced datasets."
    ),
      "Household Survey Manager", "INSEE - Paris", "09/2017 - 08/2018",
    "Paris, France", c(
        "Contributed to the redesign of the Master Sample, representing the nationwide household sampling framework for INSEE surveys.",
        "Conducted large-scale sampling simulations using advanced sampling methods impacting the work of nearly 700 field interviewers.", 
        "Worked closely with a team of five statisticians to parallelize processing workflows and analyze results"
    )
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")

```



# Skills
```{r}
#| label: skills
#| output: asis
skills_data <- tibble::tribble(
  ~category,      ~skills,
  "Programming",  "Python (Pytorch, Scipy), R (Expert), SQL (Advanced)",
  "Programming",  "Docker, kubernetes, MLOPS",
  "Programming",  "Web Development, Javascript React, NextJS",
  "Languages",    "French (Native)",
  "Languages",    "English (B2) (TOEIC 895/990)"
)

# Générer le LaTeX
skills_data |>
  cvskills(category = "category", skills = "skills")

```

# Education

```{r}
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~loc, ~dates, ~details,
    "Master of Research in Mathematics, Vision and Learning (MVA)", "Polytechnique Paris", "09/2019 - 08/2020", c(
        "Highest Honors",
        "Specialized in computer vision, deep learning, reinforcement learning, kernel methods",
        "Master's thesis on statistical models for database fusion"
    ),
    "Engineering Degree in Data-Science","ENSAE - Paris France","09/2018 - 08/2020",c(
        "Highest Honors",
        "Specialized in Machine Learning"
    ),
    "Statistical Methodology Master", "University Rennes 2 - Rennes, France", "09/2013 - 08/2014", c(
        "Highest Honors",
        "Advanced coursework in statistical methods and data analysis",
        "Time series analysis, sampling survey methodology"
    ),
    "Engineering Degree in Statistics and Probabilities", "ENSAI - Rennes, France", "09/2011 - 08/2013", c(
        "Core curriculum in statistical methods and programming",
        "Teaching Assistant for Statistics and Python courses",
        "Master's thesis on Statistical Methodology for Smoothing Insurance Claims with Time Series Analysis"
    )
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```

# Projects
```{r}
#| label: Projects and Achievements
#| output: asis
tibble::tribble(
    ~project, ~institution, ~dates, ~details,
    "Automated Satellite Image Analysis", "INSEE - Paris", "Present", c(
        "Developed a full pipeline to detect building locations from Pleiades satellite images.",
        "Trained SegFormer segmentation models for high-accuracy building detection.",
        "Tracked experiments using MLFlow and hosted the solution on INSEE's Kubernetes cluster.",
        "Integrated a containerized workflow with Kubernetes (Argo Workflows and ArgoCD).",
        "Built interactive web applications with React (Observable) and GeoServer for result visualization."
    ),
    "Automated Study Reporting System", "INSEE - Paris", "Present", c(
        "Designed and implemented a comprehensive pipeline for automating study report production using R.",
        "Developed and published the 'BoutadE' R package on GitHub, enabling rapid, reproducible reporting workflows.",
        "Automated content generation with local LLMs hosted on INSEE's Kubernetes cluster.",
        "Integrated advanced visualizations and dashboards."
    ),
    "Hackathon Winner", "EY Paris", "2018", c(
        "Led team of 4 to victory among  20 competing teams.",
        "Implemented solution using Random Forests in Python."
    )
) |>
    cvevents(when = "dates", what = "project", where = "institution", details = "details")
```
