---
author: Clément Guillo
format:
  classic-cv-pdf: default
cvcolor: 58748F
cvfont: raleway
execute:
  echo: false
---


```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```


+33 (0)6 19 93 25 36
guillo.clement@gmail.com
linkedin.com/in/clgui23
github.com/clement2323

# Profile

Data Scientist with extensive experience in spatial statistics and deep learning applications, seeking challenging position in statistical methodology and data analysis. Proven track record in implementing large-scale data processing solutions and leading cross-functional teams.

# Core Skills

- Statistical Analysis: Spatial statistics, Deep Learning, Time series analysis
- Programming: Python, R, C++, Java, SQL, PostGIS
- Development: JavaScript, React, NextJS
- Tools: LaTeX, Linux, Git

# Professional Experience

```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Head of Statistical Service", "INSEE Antilles-Guyane", "09/2023 - Present",
    "Guadeloupe, France", c(
        "Modernized production practices across 3 territories, improving efficiency by 25%",
        "Implemented machine learning algorithms for population census, processing 100,000+ satellite images",
        "Developed and delivered R training program for 20+ staff members"
    ),
    
    "Head of Spatial Statistics Methods", "INSEE", "09/2019 - 08/2023",
    "Paris, France", c(
        "Led development of deep learning models achieving 90% accuracy in satellite image segmentation",
        "Managed redesign of georeferencing system affecting 67 million addresses",
        "Supervised statistical disclosure control for 500+ business surveys annually"
    ),
    
    "Data Science Intern", "WESTAT", "07/2019 - 09/2019",
    "Rockville, Maryland, USA", c(
        "Developed alternative estimation methods for rare events using Zero-Inflated Poisson Models",
        "Analyzed imbalanced datasets with 100,000+ observations",
        "Implemented EM algorithm improving prediction accuracy by 15%"
    ),
    
    "Household Survey Manager", "INSEE", "09/2017 - 08/2018",
    "Paris, France", c(
        "Optimized R codebase reducing processing time by 40%",
        "Managed redesign of Master Sample affecting 200,000+ households",
        "Coordinated team of 5 statisticians for large-scale simulations"
    ),
    
    "Financial Institutions Account Manager", "INSEE", "09/2014 - 08/2017",
    "Paris, France", c(
        "Analyzed financial data from 1,000+ institutions",
        "Produced quarterly statistical reports for national accounts",
        "Developed automated data validation procedures"
    )
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r}
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Master of Research in Mathematics, Vision and Learning (MVA)", "ENS Paris-Saclay", "Paris, France", "09/2019 - 08/2020", c(
        "GPA: 4.0/4.0 (Highest Honors)",
        "Specialized in machine learning and computer vision",
        "Research thesis on statistical models for database fusion"
    ),
    
    "Statistical Methodology Master", "ENSAE", "Paris, France", "09/2018 - 08/2020", c(
        "GPA: 3.9/4.0 (Highest Honors)",
        "Advanced coursework in statistical methods and data analysis",
        "Selected for competitive data science track"
    ),
    
    "Engineering Degree in Statistics", "ENSAI", "Rennes, France", "09/2011 - 08/2013", c(
        "Core curriculum in statistical methods and programming",
        "Specialized in data processing and analysis",
        "Teaching Assistant for Statistics and Python courses"
    )
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```

# Projects & Achievements

```{r}
#| label: Projects & Achievements
#| output: asis
tibble::tribble(
    ~project, ~institution, ~dates, ~details,
    "Research Project", "ENSAE", "2019 - 2020", c(
        "Developed novel statistical models for database fusion",
        "Published findings in departmental research journal",
        "Presented results at student research symposium"
    ),
    
    "Hackathon Winner", "EY Paris", "2018", c(
        "Led team of 4 to victory among 50+ competing teams",
        "Developed machine learning model with 85% prediction accuracy",
        "Implemented solution using Random Forests in Python"
    )
) |>
    cvevents(when = "dates", what = "project", where = "institution", details = "details")
```

